### 2007-01-10 Documentation/part2.tex
*** empty log message ***

While it is comparatively simple to define a general neutrino source 
and to compute the oscillation physics, the general properties of a detector simulation are much more complicated. The basic assumption in building an abstract detector description is \emph{linearity}, \ie , that two neutrino events do not interfere with each other. Furthermore it is assumed that all information on the oscillation physics 
is given by the \emph{reconstructed} flavor and energy of a 
neutrino event. The term ``reconstructed'' implies that the well-defined energy of the incident neutrino, which can not be directly observed, translates via secondary particles and the detection properties into a distribution of possible energy values. This process is illustrated in \figu{distro} for the energy variable. 
%
\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.6\textwidth]{mapping}
\end{center}
\caption{\label{fig:distro} A detector maps a true parameter value onto
a distribution of reconstructed parameter values. This is illustrated here for there energy.}
\end{figure}
% 
The same, in principle, applies to the nature of the neutrino flavor. However, in this case only discrete values are applicable. Note that the reconstructed neutrino energy and the neutrino flavor are the only observables in \GLOBES .

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=13cm]{AEDL1}
\end{center}
\caption{\label{fig:channel} General concept of a ``channel''.}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=8cm]{SignalBackground}
\end{center}
\caption{\label{fig:rule} General concept of a ``rule''.}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=9cm]{Rules}
\end{center}
\caption{\label{fig:experiment} General concept of an ``experiment''.}
\end{figure}

@@

{\tt flux(\#mu\_plus)<\\

@@

We now give a short introduction to the syntax of AEDL.
 The first eight characters have to be {\tt \%!GLoBES}
in order to avoid parsing megabytes of chunk
 and producing thousands of error messages.  In addition, the version of the minimum
\GLOBES\ version the \AEDL\ file is running with has to be defined by {\tt \$version}, such as
{\tt \$version="3.0.0"}.
\index{aedl}{version@{\tt \$version}}
%
Comments can be used such as in C:
\begin{quote}
{\tt /* This starts a comment\\
 and here the comment ends */ \\
// Another comment
}
\end{quote}
There are pre-defined variables which all start with {\tt \$}. Their range
is also checked. For example,  {\tt 
\$bins} can be only between $0$ and $500$.\footnote{The upper limit is 
only there for safety reasons, the memory is allocated dynamically.} If one uses a {\tt float} quantity where  an {\tt int} is expected, the {\tt float} will be converted to an {\tt int} in the same way as in C.  For example, we have scalar variables
\begin{quote}
{\tt
\$bins = 10\\
\$baseline = 1200.0
}
\end{quote}
and simple lists
\begin{quote}
{\tt
\$densitytab=\{1.0,2.2343,3.3432\} 
}
\end{quote}
%
Since there are often groups of data which we want to refer to later,
environments can be used. This is illustrated 
with the channel definition part:
\begin{quote}
{\tt channel(\#ch1)<\\
\tb  $\ldots$\\
>
}
\end{quote}
The first part is the type of environment, which is {\tt channel} here. 
There are the following types of environments in AEDL:
\begin{quote}
{\tt flux\\
cross\\
channel\\
energy\\
rule
}
\end{quote}
Besides the environment type, there is a user-defined name 
beginning with {\tt \#}
in the above example: {\tt \#ch1}. It can be used later to refer to the 
channel defined in {\tt <$\ldots$>}. Those names are so-called 
``automatic variables'' and have to start with {\tt \#}. Note that these names have to be unique and can only be refered to after their definition.
However, similar to C, one can give a declaration without definition before:
\begin{quote}
{\tt    channel(\#ch2)<>}
\end{quote}
Now one can refer to the name {\tt \#ch2}, while the actual channel definition comes later. The internal representation of this automatic
variable is a number, which obtains its value from a counter for each type of environment. For example, for {\tt channel} the counter is {\tt numofchannels}. The counter keeps track of how many different names 
there are for one type of environment, which means that it counts the number of channels, rules, energy resolution functions \etc . Thus, the automatic
variables are numbered in the order of their definition, and the number
can later be used to refer to them in the C code (from $0$ to {\tt numof...}$-1$). In order to facilitate the the mapping from names in AEDL to indices
in C there are two functions \GLB{NameToValue} and \GLB{ValueToName} which
make this transition (see \Sec~\ref{sec:aedl_names}, 
page~\pageref{sec:aedl_names}).

@@

In this chapter, we give a detailed definition of the AEDL features. We also show the underlying mathematical concepts, where applicable. We do not exactly follow the separation of source, oscillation, and detection properties, since most issues more or less involve the detection. Instead,
we illustrate many of the features of the \GLOBES\ simulation successively
in the logical order of their definition, and demonstrate how they translate into AEDL .

@@

Before we come to the definition of the source properties, let us discuss
the total integrated luminosity of the experiment. In \GLOBES , the total number of events is in general proportional to the product of
\begin{equation}
\mathrm{Fid.~detector~mass}\,\left[\mathrm{kt/t}\right]\times 
\mathrm{Running~time} \,\left[\mathrm{yr}\right]\times\left\{ \begin{array}{c}
\mathrm{Source~power}\,\left[\mathrm{MW/GW}\right]\\
\mathrm{Useful~muon~decays}\,\left[\mathrm{yr}^{-1}\right]
\end{array}\right.\,.
\end{equation}
Thus, the source power corresponds to either the amount of energy produced per time frame in the target (such as for nuclear reactors or sources based on pion decay), or the useful muon decays per time frame (neutrino factories). In addition, the definition of the source power makes only sense together with the flux normalization, the running time, and fiducial detector mass in order to define the total integrated luminosity. Therefore, one can, in principle, use arbitrary units for these components as long as their product gives the wanted neutrino flux. However, it is
recommended to use normalizations such that the source power units are $\mathrm{MW}$ for a proton-based beam, and $\mathrm{GW}_\mathrm{thermal}$ for a reactor experiment. Correspondingly, the detector mass units should be kilotons for a proton-based beam, and tons for a reactor experiment. In any case it is a good
idea to document the choices made by the user by corresponding comments
in \AEDL.

@@

\index{aedl}{{\tt flux}!time@{\tt "@time}}
There are two principal ways to initialize a neutrino flux: 
Either one can use 
a built-in source, or one can provide a file. In both cases,
a flux is defined by the environment {\tt flux}, such as
\index{aedl}{{\tt flux}}
\begin{quote}
  {\tt flux(\#name)<\\
\tb $\ldots$\\
\tb @time = 8.0 \\
>}
\end{quote}
with a running time of $8$ years. Note that the running time is used within
the {\tt flux} environment. This feature can be used to load the neutrino and antineutrino fluxes separately, in order to combine them with different
running times within one experiment. The name of the flux {\tt \#name} will later be refered to in the channel definitions.

For a built-in neutrino source, one has to specify which
built-in spectrum has to be used, as well as its parameters. The software
will then automatically calculate the neutrino spectrum. Note that in this
case, there is no degree of freedom in the choice of the source units.
Currently, two built-in fluxes are available: $\mu^+$-decay ({\tt @builtin = 1}) and $\mu^-$-decay ({\tt @builtin = 2}). In these cases, the muon energy (enery of the parent particle) has to be specified together with the number of useful decays  per year. Thus, an example to set up a neutrino factory flux is
\index{aedl}{{\tt flux}!builtin@{\tt "@builtin}}
\index{aedl}{{\tt flux}!parent energy@{\tt "@parent\_energy}}
\index{aedl}{{\tt flux}!stored muons@{\tt "@stored\_muons}}
\begin{quote}
{\tt flux(\#mu\_plus)<\\
\tb  @builtin = 1\\
\tb  @parent\_energy = 50.0\\
\tb  @stored\_muons = 5.33e+20\\
\tb  @time = 8.0\\
>}
\end{quote}
%
\index{aedl}{{\tt flux}!power@{\tt "@power}}
\index{aedl}{{\tt flux}!norm@{\tt "@norm}}
\index{aedl}{{\tt flux}!flux file@{\tt "@flux\_file}}
For a user-defined flux, one has to give it the file name:
\begin{quote}
{\tt flux(\#user)<}\\
{\tt \tb @flux\_file = "user\_file\_1.dat"\\
\tb @time = 2.0\\
\tb @power = 4.0\\
\tb @norm = 1e+8}\\
{\tt >}
\end{quote}
In this case, the {\tt @norm} variable is an overall normalization which defines a conversion factor from the fluxes in the file to the units in \GLOBES . In general, there are many ways to give the source power of a 
neutrino source, such as neutrinos per proton on target per area per time frame. Right now, each flux has its own normalization factor, which is
not always straightfoward to calculate. Often, one has to take into account
many things, such as the number of target particles per unit mass. 
In addition, the fluxes will be rescaled by $1/L^2$, which means that the
normalization must contain a factor $L_0^2$. Here $L_0$ is the distance from the source for which the flux is given to the actual neutrino production region. At the end, it is left to the user to ensure that the 
numbers in the flux file give, after the multiplication with {\tt @norm}, 
the proper numbers of produced neutrinos corresponding to the chosen target power {\tt @power}. Usually this adjustment of {\tt @norm} is performed by comparison with known energy spectra for a specific experiment.

@@

The flux files accept one-line comments, which start
with {\tt \#} and end with the linefeed character `\verb+\n+', they are
not counted as a line and their content is discarded. This comments
are useful to provide meta information about the fluxes like units
or the origin of the information. This is also the default method
to point the user to the references he/she should to cite when using
a particular flux.\index{norm}{Flux!file!comments in}
\index{norm}{Referencing!flux data}

@@

\begin{table}[t!]
\begin{tabular}{|clp{7cm}|}
\hline
{\tt \$profiletype} & Additional variables & Description \\ 
\hline
$1$ & {\tt \$baseline} & Average density (constant) \\
$2$ & {\tt \$baseline}, {\tt \$densitysteps} & PREM profile with given number of equidistant steps \\
$3$ & {\tt \$lengthtab},  {\tt \$densitytab} & Arbitrary profile (table of layer thicknesses, table of densities) \\
\hline
\end{tabular}
\caption{\label{tab:profiletypes} Different matter density profiles which can be used with \GLOBES .}
\end{table}

@@

\begin{figure}[t!]
\begin{center}
\includegraphics[width=15cm]{energies}
\end{center}
\caption{\label{fig:energies} The different evaluation levels for the energy smearing in \GLOBES .}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
\begin{table}[t!]
\begin{center}
\begin{tabular}[h]{|c|cccc|c|l|}
\hline
Error dimension&$a$&$b$&$c$&$d$&Tilt/Calibration&Remarks\\
\hline
\hline
0&+&+&+&+&T&Systematics with tilt\\
2&-&-&-&-&-&No systematics\\
4&+&+&+&+&T&Total rates\\
7& $\infty$ &-& $\infty$ &-&-&Spectrum only\\
8&-&-&-&-&-&Total rates, no systematics\\
9&+&+&+&+&C&Systematics with calibration\\
20&?&?&?&?&?&User-defined systematics\\
\hline
\end{tabular}
\caption[Table of error dimensions]{\label{tab:error_dim}
Possible values of the error dimensions variable in \GLOBES\ and their meaning. If a parameter is designated with $+$, it will
be marginalized over, and therefore the corresponding error needs to 
have a non-zero value. If the cases with ``total rates'' in the remarks, 
the summation over the bins is performed \emph{before} computing 
the $\chi^2$, \ie, no spectral information is used. 
The error dimension~7 ``spectrum only'' leaves the 
normalization free ($\sigma_a=\sigma_c=\infty$), and therefore 
only the spectral information is used. As a consequence,
the settings for the normalization error will be ignored (designated 
with the symbol $\infty$).

>>>>

While it is comparatively simple to define a general neutrino source 
and to compute the oscillation physics, the general properties of a detector simulation are much more complicated. The basic assumption in building an abstract detector description is \emph{linearity}, \ie , that two neutrino events do not interfere with each other. Furthermore it is assumed that all information on the oscillation physics 
is given by the \emph{reconstructed} flavor and energy of a 
neutrino event. The term ``reconstructed'' implies that the well-defined energy of the incident neutrino, which can not be directly observed, translates via secondary particles and the detection properties into a distribution of possible energy values. This process is illustrated in \figu{distro} for the energy variable. 
%
\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.6\textwidth]{mapping}
\end{center}
\mycaption{\label{fig:distro} A detector maps a true parameter value onto
a distribution of reconstructed parameter values. This is illustrated here for there energy.}
\end{figure}
% 
The same, in principle, applies to the nature of the neutrino flavor. However, in this case only discrete values are applicable. Note that the reconstructed neutrino energy and the neutrino flavor are the only observables in \GLOBES .

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=13cm]{AEDL1}
\end{center}
\mycaption{\label{fig:channel} General concept of a ``channel''.}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=8cm]{SignalBackground}
\end{center}
\mycaption{\label{fig:rule} General concept of a ``rule''.}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=9cm]{Rules}
\end{center}
\mycaption{\label{fig:experiment} General concept of an ``experiment''.}
\end{figure}

@@

{\tt nuflux(\#mu\_plus)<\\

@@

We now give a short introduction to the syntax of AEDL.
 The first eight characters have to be {\tt \%!GLoBES}
in order to avoid parsing megabytes of chunk
 and producing thousands of error messages.  In addition, the version of the minimum
\GLOBES\ version the \AEDL\ file is running with has to be defined by {\tt \$version}, such as
{\tt \$version="3.0.0"}.
\index{aedl}{version@{\tt \$version}}
%
Comments can be used such as in C:
\begin{quote}
{\tt /* This starts a comment\\
 and here the comment ends */ \\
// Another comment
}
\end{quote}
There are pre-defined variables which all start with {\tt \$}. Their range
is also checked. For example,  {\tt 
\$bins} can be only between $0$ and $500$.\footnote{The upper limit is 
only there for safety reasons, the memory is allocated dynamically.} If one uses a {\tt float} quantity where  an {\tt int} is expected, the {\tt float} will be converted to an {\tt int} in the same way as in C.  For example, we have scalar variables
\begin{quote}
{\tt
\$bins = 10\\
\$baseline = 1200.0
}
\end{quote}
and simple lists
\begin{quote}
{\tt
\$densitytab=\{1.0,2.2343,3.3432\} 
}
\end{quote}
%
Since there are often groups of data which we want to refer to later,
environments can be used. This is illustrated 
with the channel definition part:
\begin{quote}
{\tt channel(\#ch1)<\\
\tb  $\ldots$\\
>
}
\end{quote}
The first part is the type of environment, which is {\tt channel} here. 
There are the following types of environments in AEDL:
\begin{quote}
{\tt nuflux\\
cross\\
channel\\
energy\\
rule
}
\end{quote}
Besides the environment type, there is a user-defined name 
beginning with {\tt \#}
in the above example: {\tt \#ch1}. It can be used later to refer to the 
channel defined in {\tt <$\ldots$>}. Those names are so-called 
``automatic variables'' and have to start with {\tt \#}. Note that these names have to be unique and can only be refered to after their definition.
However, similar to C, one can give a declaration without definition before:
\begin{quote}
{\tt    channel(\#ch2)<>}
\end{quote}
Now one can refer to the name {\tt \#ch2}, while the actual channel definition comes later. The internal representation of this automatic
variable is a number, which obtains its value from a counter for each type of environment. For example, for {\tt channel} the counter is {\tt numofchannels}. The counter keeps track of how many different names 
there are for one type of environment, which means that it counts the number of channels, rules, energy resolution functions \etc . Thus, the automatic
variables are numbered in the order of their definition, and the number
can later be used to refer to them in the C code (from $0$ to {\tt numof...}$-1$). In order to facilitate the the mapping from names in AEDL to indices
in C there are two functions \GLB{NameToValue} and \GLB{ValueToName} which
make this transition (see \Sec~\ref{sec:aedl_names}, 
page~\pageref{sec:aedl_names}).

@@

In this chapter, we give a detailed definition of the \AEDL\ features. We also show the underlying mathematical concepts, where applicable. We do not exactly follow the separation of source, oscillation, and detection properties, since most issues more or less involve the detection. Instead,
we illustrate many of the features of the \GLOBES\ simulation successively
in the logical order of their definition, and demonstrate how they translate into \AEDL .

@@

Before we come to the definition of the source properties, let us discuss
the total integrated luminosity of the experiment. In \GLOBES , the total number of events is in general proportional to the product of
\begin{equation}
\mathrm{Fid.~detector~mass}\,\left[\mathrm{kt/t}\right]\times 
\mathrm{Running~time} \,\left[\mathrm{yr}\right]\times\left\{ \begin{array}{c}
\mathrm{Source~power}\,\left[\mathrm{MW/GW}\right]\\
\mathrm{Useful~parent~decays}\,\left[\mathrm{yr}^{-1}\right]
\end{array}\right.\,.
\end{equation}
Thus, the source power corresponds to either the amount of energy produced per time frame in the target (such as for nuclear reactors or sources based on pion decay), or the useful parent particle decays per time frame (neutrino factories, beta beams). In addition, the definition of the source power makes only sense together with the flux normalization, the running time, and the fiducial detector mass in order to define the total integrated luminosity. Therefore, one can, in principle, use arbitrary units for these components as long as their product gives the wanted neutrino flux. However, it is
recommended to use normalizations such that the source power units are $\mathrm{MW}$ for a proton-based beam, and $\mathrm{GW}_\mathrm{thermal}$ for a reactor experiment. Correspondingly, the detector mass units should be kilotons for a proton-based beam, and tons for a reactor experiment. In any case it is a good
idea to document the choices made by the user by corresponding comments
in \AEDL. For more details on the luminosity implementation, see appendix on page~\pageref{app:flux}.

@@

\index{aedl}{{\tt nuflux}!time@{\tt "@time}}
There are two principal ways to initialize a neutrino flux: 
Either one can use 
a built-in source, or one can provide a file. In both cases,
a flux is defined by the environment {\tt nuflux}, such as
\index{aedl}{{\tt nuflux}}
\begin{quote}
  {\tt nuflux(\#name)<\\
\tb $\ldots$\\
\tb @time = 8.0 \\
>}
\end{quote}
with a running time of $8$ years. Note that the running time is used within
the {\tt nuflux} environment. This feature can be used to load the neutrino and antineutrino fluxes separately, in order to combine them with different
running times within one experiment. The name of the flux {\tt \#name} will later be referred to in the channel definitions. Note that \GLOBES\ versions older than 3.0 use the still supported {\tt flux} environment, which is different from {\tt nuflux} by an undocumented normalization factor 5.2 for user-defined fluxes. This difference is explained in the appendix on page~\pageref{app:flux}.

\index{aedl}{{\tt flux}}

\begin{table}[t]
\begin{center}
\begin{tabular}{|cllc|}
\hline
{\tt @builtin} & Description & Parameters & Min. version \\
\hline
1 & Neutrino factory $\mu^+$ decay & {\tt @parent\_energy} [GeV], & 2.0 \\
& & {\tt @stored\_muons} &  \\
2 & Neutrino factory $\mu^-$ decay & {\tt @parent\_energy} [GeV], & 2.0 \\
& & {\tt @stored\_muons} &  \\
3 & Beta beam, inv. beta decay & {\tt @end\_point} [GeV], & 3.0 \\
& & {\tt @stored\_ions}, &  \\
& & {\tt @gamma} & \\
4 & Beta beam, beta decay & {\tt @end\_point} [GeV], & 3.0 \\
& & {\tt @stored\_ions}, &  \\
& & {\tt @gamma} & \\
\hline
\end{tabular}
\end{center}
\mycaption{\label{tab:binfluxes} Built-in fluxes currently supported by \GLOBES . For details on
the beta beams, see \Ref~\cite{Huber:2005jk}. MR ABOUT BETA BEAMS: DOES THIS REALLY WORK FOR ALL ISOTOPES? IS THE DIFFERENCE BETWEEN 3 AND 4 CORRECTLY DESCRIBED? WHY IS THERE A NORMALIZATION FACTOR 50.9 IN THE FILES?}
\end{table}

For a built-in neutrino source, one has to specify which
built-in spectrum has to be used, as well as its parameters. The software
will then automatically calculate the neutrino spectrum. Note that in this
case, there is no degree of freedom in the choice of the source units.
The currently available fluxes are described in \Tab~\ref{tab:binfluxes}.
For example, two built-in neutrino factory fluxes are available: $\mu^+$-decay ({\tt @builtin = 1}) and $\mu^-$-decay ({\tt @builtin = 2}). In these cases, the muon energy (enery of the parent particle) has to be specified together with the number of useful decays  per year. Thus, an example to set up a neutrino factory flux is 
\index{aedl}{{\tt nuflux}!builtin@{\tt "@builtin}}
\index{aedl}{{\tt nuflux}!parent energy@{\tt "@parent\_energy}}
\index{aedl}{{\tt nuflux}!stored muons@{\tt "@stored\_muons}}
\index{aedl}{{\tt nuflux}!end point@{\tt "@end\_point}}
\index{aedl}{{\tt nuflux}!stored ions@{\tt "@stored\_ions}}
\index{aedl}{{\tt nuflux}!gamma@{\tt "@gamma}}
\begin{quote}
{\tt nuflux(\#mu\_plus)<\\
\tb  @builtin = 1\\
\tb  @parent\_energy = 50.0\\
\tb  @stored\_muons = 5.33e+20\\
\tb  @time = 8.0\\
>}
\end{quote}
%
\index{aedl}{{\tt nuflux}!power@{\tt "@power}}
\index{aedl}{{\tt nuflux}!norm@{\tt "@norm}}
\index{aedl}{{\tt nuflux}!flux file@{\tt "@flux\_file}}
For a user-defined flux, one has to give it the file name:
\begin{quote}
{\tt nuflux(\#user)<}\\
{\tt \tb @flux\_file = "user\_file\_1.dat"\\
\tb @time = 2.0\\
\tb @power = 4.0\\
\tb @norm = 1e+8}\\
{\tt >}
\end{quote}
In this case, the {\tt @norm} variable is an overall normalization which defines a conversion factor from the fluxes in the file to the units in \GLOBES . In general, there are many ways to give the source power of a 
neutrino source, such as neutrinos per proton on target per area per time frame. Right now, each flux has its own normalization factor, which is
not always straightfoward to calculate. Often, one has to take into account
many things, such as the number of target particles per unit mass. 
In addition, the fluxes will be rescaled by $1/L^2$, which means that the
normalization must contain a factor $L_0^2$. Here $L_0$ is the distance from the source for which the flux is given to the actual neutrino production region. At the end, it is left to the user to ensure that the 
numbers in the flux file give, after the multiplication with {\tt @norm}, 
the proper numbers of produced neutrinos corresponding to the chosen target power {\tt @power}. Usually this adjustment of {\tt @norm} is performed by comparison with known energy spectra for a specific experiment.
For more details on the flux definition, see appendix on page~\pageref{app:flux}.

@@

The flux files accept one-line comments, which start
with {\tt \#} and end with the linefeed character `\verb+\n+', they are
not counted as a line and their content is discarded. These comments
are useful to provide meta information about the fluxes such as units
or the origin of the information. This is also the default method
to point the user to the references one should to cite when using
a particular flux.\index{norm}{Flux!file!comments in}
\index{norm}{Referencing!flux data}

@@

\begin{table}[t!]
\begin{tabular}{|clp{7cm}|}
\hline
{\tt \$profiletype} & Additional variables & Description \\ 
\hline
$1$ & {\tt \$baseline} & Average density (constant) \\
$2$ & {\tt \$baseline}, {\tt \$densitysteps} & PREM profile with given number of equidistant steps \\
$3$ & {\tt \$lengthtab},  {\tt \$densitytab} & Arbitrary profile (table of layer thicknesses, table of densities) \\
\hline
\end{tabular}
\mycaption{\label{tab:profiletypes} Different matter density profiles which can be used with \GLOBES .}
\end{table}

@@

\begin{figure}[t!]
\begin{center}
\includegraphics[width=15cm]{energies}
\end{center}
\mycaption{\label{fig:energies} The different evaluation levels for the energy smearing in \GLOBES .}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
\begin{table}[t!]
\begin{center}
\begin{tabular}[h]{|c|cccc|c|l|}
\hline
Error dimension&$a$&$b$&$c$&$d$&Tilt/Calibration&Remarks\\
\hline
\hline
0&+&+&+&+&T&Systematics with tilt\\
2&-&-&-&-&-&No systematics\\
4&+&+&+&+&T&Total rates\\
7& $\infty$ &-& $\infty$ &-&-&Spectrum only\\
8&-&-&-&-&-&Total rates, no systematics\\
9&+&+&+&+&C&Systematics with calibration\\
20&?&?&?&?&?&User-defined systematics\\
\hline
\end{tabular}
\mycaption[Table of error dimensions]{\label{tab:error_dim}
Possible values of the error dimensions variable in \GLOBES\ and their meaning. If a parameter is designated with $+$, it will
be marginalized over, and therefore the corresponding error needs to 
have a non-zero value. If the cases with ``total rates'' in the remarks, 
the summation over the bins is performed \emph{before} computing 
the $\chi^2$, \ie, no spectral information is used. 
The error dimension~7 ``spectrum only'' leaves the 
normalization free ($\sigma_a=\sigma_c=\infty$), and therefore 
only the spectral information is used. As a consequence,
the settings for the normalization error will be ignored (designated 
with the symbol $\infty$).
